Multi-scale assessment of a grassland productivity model

### 2020-06-16 manuscript/manuscript.Rmd
add supplement site table

bibliography: refs
running:
  title: Extended PhenoGrass Evaluation
  author: Taylor & Browning
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  Copyright 2020 The Authors
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
availability:
  codedata: |
    All code and data used in the analysis is available in the repository at https://github.com/sdtaylor/PhenograssReplication, the PhenoGrass model is implemented in a python package https://github.com/sdtaylor/GrasslandModels. Both are archived permanently on Zenodo (link).
authorcontribution: |
  Shawn concieved of the project. Shawn and Dawn wrote the paper.
acknowledgements: |
  None
appendix: |
  Appendix: TODO
output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---

>>>>

bibliography: refs
running:
  title: Extended PhenoGrass Evaluation
  author: Taylor & Browning
# This section is mandatory even if you declare that no competing interests are present.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  Copyright 2020 The Authors
### The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
### It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
availability:
  codedata: |
    All code and data used in the analysis is available in the repository at https://github.com/sdtaylor/PhenograssReplication, the PhenoGrass model is implemented in a python package https://github.com/sdtaylor/GrasslandModels. Both are archived permanently on Zenodo (link).
authorcontribution: |
  Shawn concieved of the project. Shawn and Dawn wrote the paper.
acknowledgements: |
  None
appendix: |
  \section{Tables in Appendix}
  \appendixtables
  \begin{table}
  \caption{Sites used in analysis. A * indicates the site was also used in the original analysis.}
  \small
  \begin{tabular}{l|r|r|l|r|l|l|r|l}
  \hline
  name & lat & lon & vegetation & roi id & first date & last date & site years & ecoregion\\
  \hline
  ahwahnee & 37.75 & -119.58 & GR & 3000 & 2015-07-28 & 2020-03-05 & 4.6 & NWForests\\
  \hline
  archboldavir & 27.18 & -81.22 & AG & 1000 & 2016-11-18 & 2020-03-05 & 3.1 & ETempForests\\
  \hline
  archboldavirx & 27.17 & -81.22 & AG & 1000 & 2016-05-16 & 2020-03-05 & 3.6 & ETempForests\\
  \hline
  archboldpnot & 27.19 & -81.20 & AG & 1000 & 2016-05-13 & 2020-03-05 & 3.6 & ETempForests\\
  \hline
  archboldpnotx & 27.18 & -81.20 & AG & 1000 & 2016-05-16 & 2020-03-05 & 3.6 & ETempForests\\
  \hline
  arsgacp1 & 31.51 & -83.62 & AG & 1000 & 2016-05-10 & 2020-03-05 & 3.8 & ETempForests\\
  \hline
  arsmnswanlake1 & 45.68 & -95.80 & AG & 1000 & 2015-10-02 & 2020-03-05 & 4.4 & GrPlains\\
  \hline
  bullshoals & 36.56 & -93.07 & GR & 1000 & 2013-11-19 & 2020-03-05 & 5.8 & ETempForests\\
  \hline
  burnssagebrush & 43.47 & -119.69 & SH & 1000 & 2012-10-13 & 2020-03-05 & 7.3 & NADeserts\\
  \hline
  butte* & 45.95 & -112.48 & GR & 1000 & 2009-01-11 & 2020-03-05 & 10.7 & NWForests\\
  \hline
  cperagm & 40.84 & -104.77 & AG & 1000 & 2016-05-19 & 2020-03-05 & 3.8 & GrPlains\\
  \hline
  cperagm & 40.84 & -104.77 & GR & 1000 & 2016-05-19 & 2020-03-05 & 3.8 & GrPlains\\
  \hline
  cpertgm & 40.83 & -104.76 & GR & 1000 & 2016-05-04 & 2020-03-05 & 3.8 & GrPlains\\
  \hline
  cperuvb & 40.81 & -104.76 & GR & 1000 & 2015-07-16 & 2020-03-05 & 4.7 & GrPlains\\
  \hline
  gatesofthemountains & 46.83 & -111.71 & GR & 2000 & 2011-08-12 & 2019-02-01 & 7.1 & NWForests\\
  \hline
  glacier & 48.50 & -113.99 & GR & 1000 & 2009-02-07 & 2020-03-05 & 11.0 & NWForests\\
  \hline
  goodwater & 39.23 & -92.12 & AG & 1001 & 2015-09-26 & 2020-03-05 & 4.5 & GrPlains\\
  \hline
  grandteton & 43.92 & -110.58 & SH & 1000 & 2015-07-28 & 2020-02-04 & 3.5 & NWForests\\
  \hline
  harvardfarmnorth & 42.52 & -72.18 & AG & 1000 & 2015-11-07 & 2020-03-05 & 4.3 & NForest\\
  \hline
  harvardfarmsouth & 42.52 & -72.18 & AG & 1000 & 2015-11-07 & 2020-03-05 & 4.3 & NForest\\
  \hline
  harvardgarden & 42.53 & -72.19 & AG & 1000 & 2016-06-12 & 2020-03-05 & 3.7 & NForest\\
  \hline
  hawbeckereddy & 40.66 & -77.85 & AG & 1000 & 2015-09-23 & 2019-05-14 & 3.4 & ETempForests\\
  \hline
  humnokericea & 34.59 & -91.75 & AG & 1000 & 2015-06-25 & 2020-03-05 & 4.2 & ETempForests\\
  \hline
  humnokericec & 34.59 & -91.75 & AG & 1000 & 2015-06-25 & 2020-03-05 & 4.5 & ETempForests\\
  \hline
  ibp* & 32.59 & -106.85 & GR & 1000 & 2014-02-16 & 2020-03-05 & 6.0 & NADeserts\\
  \hline
  ibp* & 32.59 & -106.85 & SH & 1001 & 2014-02-16 & 2020-03-02 & 6.0 & NADeserts\\
  \hline
  jasperridge* & 37.40 & -122.22 & GR & 1000 & 2012-03-08 & 2017-03-09 & 5.0 & MWCoastForests\\
  \hline
  jasperridge* & 37.40 & -122.22 & GR & 2000 & 2017-03-18 & 2020-03-05 & 3.0 & MWCoastForests\\
  \hline
  jerbajada & 32.58 & -106.63 & SH & 1000 & 2014-04-20 & 2020-03-05 & 5.9 & NADeserts\\
  \hline
  jernort & 32.62 & -106.79 & SH & 2000 & 2016-10-28 & 2020-03-05 & 3.3 & NADeserts\\
  \hline
  jersand & 32.52 & -106.80 & SH & 1000 & 2014-02-28 & 2020-03-05 & 6.0 & NADeserts\\
  \hline
  kansas* & 39.06 & -95.19 & GR & 1000 & 2012-12-03 & 2019-12-31 & 6.7 & GrPlains\\
  \hline
  kaweah & 36.44 & -118.91 & SH & 1000 & 2011-07-13 & 2019-09-20 & 8.2 & MedCA\\
  \hline
  kelloggcorn & 42.44 & -85.32 & AG & 1000 & 2014-05-23 & 2019-10-05 & 4.9 & ETempForests\\
  \hline
  \end{tabular}
  \end{table}

  \begin{table}
  \caption{Sites used continued}
  \small
  \begin{tabular}{l|r|r|l|r|l|l|r|l}
  \hline
  name & lat & lon & vegetation & roi id & first date & last date & site years & ecoregion\\
  \hline
  kelloggcorn2 & 42.40 & -85.38 & AG & 1000 & 2015-07-16 & 2019-04-11 & 3.2 & ETempForests\\
  \hline
  kelloggcorn3 & 42.40 & -85.37 & AG & 1000 & 2015-07-16 & 2020-03-05 & 3.7 & ETempForests\\
  \hline
  kelloggcornsoy2 & 42.40 & -85.37 & AG & 1000 & 2015-07-16 & 2020-03-05 & 3.7 & ETempForests\\
  \hline
  kelloggmiscanthus & 42.40 & -85.38 & AG & 1000 & 2015-07-16 & 2020-03-05 & 3.7 & ETempForests\\
  \hline
  kelloggoldfield & 42.40 & -85.37 & AG & 1000 & 2015-07-16 & 2020-03-05 & 4.2 & ETempForests\\
  \hline
  kendall* & 31.74 & -109.94 & GR & 1000 & 2012-07-06 & 2020-03-05 & 7.6 & SouthAridHighliands\\
  \hline
  kendall* & 31.74 & -109.94 & SH & 1000 & 2012-08-08 & 2019-11-07 & 7.2 & SouthAridHighliands\\
  \hline
  konza* & 39.08 & -96.56 & GR & 1000 & 2012-03-17 & 2019-12-19 & 6.2 & GrPlains\\
  \hline
  lethbridge* & 49.71 & -112.94 & GR & 1000 & 2011-12-07 & 2020-03-05 & 8.3 & GrPlains\\
  \hline
  luckyhills & 31.74 & -110.05 & SH & 2000 & 2015-01-26 & 2018-06-04 & 3.4 & SouthAridHighliands\\
  \hline
  mandanh5 & 46.78 & -100.95 & AG & 1000 & 2015-09-17 & 2020-03-05 & 4.5 & GrPlains\\
  \hline
  mandani2 & 46.76 & -100.93 & AG & 1000 & 2016-04-22 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  manilacotton & 35.89 & -90.14 & AG & 1000 & 2016-06-21 & 2020-03-05 & 3.6 & ETempForests\\
  \hline
  marena* & 36.06 & -97.21 & GR & 1000 & 2012-06-12 & 2018-06-19 & 5.8 & GrPlains\\
  \hline
  mead1 & 41.17 & -96.48 & AG & 1000 & 2016-07-12 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  mead2 & 41.16 & -96.47 & AG & 1000 & 2016-07-12 & 2020-03-05 & 3.6 & GrPlains\\
  \hline
  mead3 & 41.18 & -96.44 & AG & 1000 & 2016-07-12 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  meadpasture & 41.14 & -96.46 & AG & 1000 & 2016-07-15 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  monture* & 47.02 & -113.13 & GR & 2000 & 2010-11-04 & 2019-02-01 & 8.0 & NWForests\\
  \hline
  mtrobson & 53.03 & -119.20 & GR & 1000 & 2015-02-16 & 2020-03-05 & 4.8 & NWForests\\
  \hline
  nationalelkrefuge & 43.49 & -110.74 & GR & 1000 & 2015-08-12 & 2020-03-05 & 4.5 & NWForests\\
  \hline
  NEON.D03.DSNY. & 28.13 & -81.44 & GR & 1000 & 2016-12-15 & 2020-03-05 & 3.2 & ETempForests\\
  \hline
  NEON.D06.KONA. & 39.11 & -96.61 & AG & 1000 & 2016-05-07 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  NEON.D06.KONZ. & 39.10 & -96.56 & GR & 1000 & 2017-02-25 & 2020-03-05 & 3.0 & GrPlains\\
  \hline
  NEON.D09.WOOD. & 47.13 & -99.24 & GR & 1000 & 2016-12-18 & 2020-03-05 & 3.2 & GrPlains\\
  \hline
  NEON.D10.ARIK. & 39.76 & -102.45 & GR & 1000 & 2016-12-18 & 2020-03-05 & 3.1 & GrPlains\\
  \hline
  NEON.D10.CPER. & 40.82 & -104.75 & GR & 1000 & 2016-06-30 & 2020-03-05 & 3.7 & GrPlains\\
  \hline
  NEON.D10.STER. & 40.46 & -103.03 & AG & 1000 & 2016-12-18 & 2020-03-05 & 3.2 & GrPlains\\
  \hline
  NEON.D11.OAES. & 35.41 & -99.06 & GR & 1000 & 2017-02-28 & 2020-03-05 & 3.0 & GrPlains\\
  \hline
  NEON.D13.MOAB. & 38.25 & -109.39 & GR & 1000 & 2017-02-25 & 2020-03-05 & 3.0 & NADeserts\\
  \hline
  NEON.D14.JORN. & 32.59 & -106.84 & GR & 1000 & 2017-02-25 & 2020-03-05 & 3.0 & NADeserts\\
  \hline
  NEON.D14.SRER. & 31.91 & -110.84 & SH & 1000 & 2017-02-25 & 2020-03-05 & 3.0 & NADeserts\\
  \hline
  NEON.D15.ONAQ. & 40.18 & -112.45 & GR & 1000 & 2016-12-18 & 2020-03-05 & 3.2 & NADeserts\\
  \hline
  NEON.D15.ONAQ. & 40.18 & -112.45 & SH & 1001 & 2016-12-18 & 2020-03-05 & 3.2 & NADeserts\\
  \hline
  oakville & 47.90 & -97.32 & GR & 1000 & 2014-08-06 & 2020-03-05 & 4.6 & GrPlains\\
  \hline
  \end{tabular}
  \end{table}

  \begin{table}
  \caption{Sites used continued}
  \small
  \begin{tabular}{l|r|r|l|r|l|l|r|l}
  \hline
  name & lat & lon & vegetation & roi id & first date & last date & site years & ecoregion\\
  \hline
  pointreyes & 38.00 & -123.02 & SH & 1000 & 2004-01-23 & 2019-03-18 & 13.3 & MedCA\\
  \hline
  rosemountnprs & 44.68 & -93.07 & AG & 1000 & 2015-10-29 & 2020-03-05 & 4.3 & GrPlains\\
  \hline
  sevilletagrass & 34.36 & -106.70 & GR & 1000 & 2014-11-07 & 2020-03-05 & 5.1 & NADeserts\\
  \hline
  sevilletashrub & 34.33 & -106.74 & SH & 1000 & 2014-10-29 & 2020-03-05 & 5.0 & NADeserts\\
  \hline
  silverton & 45.00 & -122.69 & AG & 1000 & 2013-07-22 & 2020-02-10 & 5.9 & NWForests\\
  \hline
  smokypurchase & 35.59 & -83.07 & GR & 2000 & 2016-01-02 & 2020-03-05 & 4.0 & ETempForests\\
  \hline
  southerngreatplains & 36.61 & -97.49 & AG & 1000 & 2012-05-16 & 2020-03-05 & 7.5 & GrPlains\\
  \hline
  spruceT6P16E & 47.51 & -93.45 & SH & 1000 & 2015-08-24 & 2020-03-05 & 4.6 & NForest\\
  \hline
  stjones & 39.09 & -75.44 & GR & 1000 & 2015-09-20 & 2020-03-05 & 4.4 & ETempForests\\
  \hline
  sweetbriargrass & 37.56 & -79.09 & AG & 1000 & 2016-03-23 & 2020-03-05 & 3.8 & ETempForests\\
  \hline
  teddy & 46.89 & -103.38 & GR & 1000 & 2010-01-02 & 2019-03-27 & 8.5 & GrPlains\\
  \hline
  teddy & 46.89 & -103.38 & SH & 1000 & 2003-05-11 & 2019-03-27 & 14.4 & GrPlains\\
  \hline
  tonzi* & 38.43 & -120.97 & GR & 1000 & 2011-10-26 & 2020-02-13 & 7.3 & MedCA\\
  \hline
  turkeypointenf02 & 42.66 & -80.56 & AG & 1000 & 2012-05-01 & 2020-03-05 & 7.5 & ETempForests\\
  \hline
  twitchell & 38.11 & -121.65 & AG & 1000 & 2011-11-16 & 2017-04-05 & 4.0 & MedCA\\
  \hline
  uiefmaize & 40.06 & -88.20 & AG & 1000 & 2008-11-06 & 2020-03-02 & 11.3 & ETempForests\\
  \hline
  uiefmiscanthus & 40.06 & -88.20 & AG & 1000 & 2008-11-12 & 2018-04-29 & 9.2 & ETempForests\\
  \hline
  uiefprairie* & 40.06 & -88.20 & GR & 1000 & 2008-10-22 & 2020-03-02 & 11.3 & ETempForests\\
  \hline
  uiefswitchgrass & 40.06 & -88.20 & AG & 1000 & 2008-10-22 & 2020-03-02 & 10.6 & ETempForests\\
  \hline
  usgseros & 43.73 & -96.62 & GR & 1000 & 2014-09-11 & 2017-10-02 & 3.1 & GrPlains\\
  \hline
  uwmfieldsta & 43.39 & -88.02 & GR & 1000 & 2013-03-15 & 2020-03-05 & 7.0 & ETempForests\\
  \hline
  vaira* & 38.41 & -120.95 & GR & 1000 & 2011-10-17 & 2020-02-28 & 7.7 & MedCA\\
  \hline
  \end{tabular}
  \end{table}

output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
---
